### 2014-06-06 writing/S'14 paper/recursion.tex
Typos fixed

% NOTE: There was some confusion at CSLI and the 224U lecture about
% whether this was theorem proving or some kind of model checking.
% Hopefully this is explicit enough.
Socher et al.~\cite{socher2012semantic} show that a matrix-vector RNN
model somewhat similar to our RNTN can learn a logic, but the logic
discussed here is a much better approximation of the kind of
expressivity needed for natural language. The logic learned in that
experiment is boolean, wherein the atomic symbols are simply the
values $0$ and $1$, rather than variables over those values. While
learning the operators of that logic is not trivial, the outputs of
each operator can be represented accurately by a single bit. The
statements of propositional logic learned here describe conditions on
unknown truth values of propositions. As opposed to the two-way
contrasts seen in \cite{socher2012semantic}, this logic distinguishes
between $2^{6} = 64$ possible assignments of truth values, and
expressions of this logic define arbitrary conditions on these
possible assignments, for a total of $2^{64}$ %($\approx 10^{20}$)
possible statements that the intermediate vector representations need
to be able to distinguish if it is to learn this logic system in its
full generality.

>>>>

% NOTE: There was some confusion at CSLI and the 224U lecture about
% whether this was theorem proving or some kind of model checking.
% Hopefully this is explicit enough.
Socher et al.~\cite{socher2012semantic} show that a matrix-vector RNN
model somewhat similar to our RNTN can learn a logic, but the logic
discussed here is a much better approximation of the kind of
expressivity needed for natural language. The logic learned in that
experiment is boolean, wherein the atomic symbols are simply the
values $0$ and $1$, rather than variables over those values. While
learning the operators of that logic is not trivial, the outputs of
each operator can be represented accurately by a single bit. The
statements of propositional logic learned here describe conditions on
unknown truth values of propositions. As opposed to the two-way
contrasts seen in \cite{socher2012semantic}, this logic distinguishes
between $2^{6} = 64$ possible assignments of truth values, and
expressions of this logic define arbitrary conditions on these
possible assignments, for a total of $2^{64}$ %($\approx 10^{20}$)
possible statements that the intermediate vector representations need
to be able to distinguish if it is to learn this logical system in its
full generality.
